Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-27 paper/manuscript.Rmd
Most changes to intro

Species interactions are known to vary widely across space and time. 
There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another. 
Some of this variation can be attributed to environmental drivers. 
However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the number of partners a species has is still unknown. 
Understanding how the number of partners—the species degree—is driven by the environment is crucial because it underpins the species role in its community and shapes the structure of the network of interactions. 
This structure, in turn, determines ecosystem function and stability.

@@

One possible explanation for the seemingly contradictory evidence is that each species can have multiple partners. 
Each of these partners, as well as the interactions with them, can be simultaneously affected by the environmental conditions. 
Therefore environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself. 
Previous research suggests that there might be two alternative hypotheses of how environmental stress may affect species degree [@tylianakis_ecological_2017]. 
On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids.

On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs. 
Therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.

Here, we investigate whether, and how, environmental stress can systematically affect species degree. 
Our main aim is to test the two competing hypotheses that relate environmental stress and species degree and investigate whether this changes across species or between trophic guilds. 
We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to engage with more partners and broaden their trophic niche. 
Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress by focusing on the most beneficial partners. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.

We test these hypotheses using data on plant-pollinator interactions. 
We use the species' patterns of occurrence to estimate the environmental suitability in their communities as an indirect measure of the environmental stress they might experience. 
Condensing the environmental variation over multiple factors (like temperature and precipitation) into a single metric is crucial to generalise our findings at a global scale.

>>>>

Species interactions are known to vary widely across space and time. 
There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another. 
Some of this variation can be attributed to environmental drivers. 
However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the species' specialisation. 
Understanding how the number of partners is driven by the environment is crucial because it underpins the species role in its community and shapes the structure of the network of interactions. 
This structure, in turn, determines ecosystem function and stability.

@@

One possible explanation for the seemingly contradictory evidence is that different bioclimatic factors (like temperature or precipitation) can have contrasting effects on species and their partners. 
Here we attempt to simplify this situation by reducing multiple factors into a single measure of environmental stress. 
Previous research suggests that environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself. 
Specifically, we proporse two alternative hypotheses of how environmental stress may affect specialisation [@tylianakis_ecological_2017]. 
On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the thropic niche breadth of parasitoids.

On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions.
Higher environmental stress is likely to be reflected in greater energetic or reproductive costs. 
Therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.

Here, we investigate whether and how environmental stress can systematically affect specialisation.  
Our main aim is to test the two aforementioned hypotheses that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds. 
We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
In other words we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment in community [which has been previously shown to be determinant factor; @gravel_bringing_2018]
We test these hypotheses using data on plant-pollinator interactions. 
This system is a particularly interesting XX.
We use the species' patterns of global occurrence to estimate the bioclimatic suitability of their communities and use this as an indirect measure of the environmental stress they might experience.
